\documentclass{article}
\usepackage{graphicx} % Required to insert images
\usepackage[hidelinks]{hyperref}

% Margins
\topmargin=-0.45in
\evensidemargin=0in
\oddsidemargin=0in
\textwidth=6.5in
\textheight=9.0in
\headsep=0.25in

\linespread{1.1} % Line spacing

\title{
\vspace{2in}
\textmd{\textbf{CPSC 471:\ Initial Draft Design}}\\
\normalsize\vspace{0.1in}\small{Due\ on\ March 21 \\ Group Number 3 \\ TA: Ibrahim Karakira}\\
\vspace{3in}
}

\author{Tanner Collin, Jordan Heinrichs, Ali Waseem}
\date{}

\begin{document}
\maketitle
\newpage

\section{Introduction}
This report contains the initial draft design and a progress report for our project Renti, a peer to peer vehicle renting service. The current progress will discuss the
technologies chosen for the framework and much work is done implementing it. As our project uses an Object Relational Mapping (ORM) to access our database we have an
object orientated model which will be outlined. Lastly, the draft of the user interface is discussed. % This is the weakest introduction yet.

\section{Current Progress and Technologies}
For the back end of the project we are using Node.js with <ALI INSERT THE LONG LIST OF JAVASCRIPT FRAMEWORKS THAT WE USE>. The database is using SQLite3 with Bookshelf.js to provide the ORM interface.
The back end is finished and the API is tested. As the front end is implemented there will likely need to be some changes to the API but it is in a state where work can be started on the front end
for the web application and possibly the mobile application.

The front end will be implemented using <INSERT MORE WEB JARGON HERE>.
The boiler plate code will be taken from Ali Waseem's blog including functions like user authentication. % Not sure if we should bother mentioning this but I have no idea what to say in this report.
Each project member will be responsible for creating components to interact with the back end API.
Work is currently started and the projected completion date for the front end is end of March.

\section{Object Orientated Model}


\section{User Interface Draft Design} % Not sure if we need this section

\section{Conclusion}

\end{document}
